### 2020-03-05 README.Rmd
fix typos

Note that upon registering the URL, hash-archive.org has returned the very same identifier, confirming this is the same content as our local copy. Such an archive is nothing more than a simple key-value store, indicating which URL(s) contain our content.  In this way, it can act much like a DOI re-direct, turing our identifier into resolvable, downloadable URL.  Unlike the DOI system though, this system is completely distributed -- we need not rely on any single authority to issue the identifier, and we need not resolve the identifier to a single location.  Thanks to the cryptographic properties of the hash, it is effectively impossible to generate a different identifier for the same content, or the same identifier for different content. We need not trust the authority of the registry, because we can always verify the content we recieve corresponds to what we wanted by comparing hashes (or hash URIs).

@@

In this case, we see more than one URL has been registered containing exactly the same content. That is not surprising, as this dataset is commonly used and reproduced. Additional useful metadata, such as the file size and timestamp the URL was registered are also reported. Notably, multiple URLs for an object could serve different purposes: we could register URLs that are more susceptible to link rot in the long term but provide higher bandwidth for downloads in the short term (e.g. S3 bucket vs scientific repository.)

It is worth noting that we still have no guarentee that these urls will not suffer link rot and cease to work -- this is not a replacement for archival storage efforts -- but the hash URI identifier allows us to avoid relying on a single storage point, and gives us a robust way to refer to an object.

@@

Content URIs are completely compatible with such location-based identifiers, indeed, there is no reason why such an identifier could not be the (or one of the) download URLs resolved by the content identifier. I think it would be ideal if data repositories such as Zenodo, Dryad, or institutional repostitories, which together offer some of our best capacity for archival storage, would register the locations of their content by such content hash uris.

>>>>

Note that upon registering the URL, hash-archive.org has returned the very same identifier, confirming this is the same content as our local copy. Such an archive is nothing more than a simple key-value store, indicating which URL(s) contain our content.  In this way, it can act much like a DOI re-direct, turing our identifier into resolvable, downloadable URL.  Unlike the DOI system though, this system is completely distributed -- we need not rely on any single authority to issue the identifier, and we need not resolve the identifier to a single location.  Thanks to the cryptographic properties of the hash, it is effectively impossible to generate a different identifier for the same content, or the same identifier for different content. We need not trust the authority of the registry, because we can always verify the content we receive corresponds to what we wanted by comparing hashes (or hash URIs).

@@

In this case, we see more than one URL has been registered containing exactly the same content. That is not surprising, as this dataset is commonly used and reproduced. Additional useful metadata, such as the file size and time-stamp the URL was registered are also reported. Notably, multiple URLs for an object could serve different purposes: we could register URLs that are more susceptible to link rot in the long term but provide higher bandwidth for downloads in the short term (e.g. S3 bucket vs scientific repository.)

It is worth noting that we still have no guarantee that these urls will not suffer link rot and cease to work -- this is not a replacement for archival storage efforts -- but the hash URI identifier allows us to avoid relying on a single storage point, and gives us a robust way to refer to an object.

@@

Content URIs are completely compatible with such location-based identifiers, indeed, there is no reason why such an identifier could not be the (or one of the) download URLs resolved by the content identifier. I think it would be ideal if data repositories such as Zenodo, Dryad, or institutional repositories, which together offer some of our best capacity for archival storage, would register the locations of their content by such content hash URIs.
